### 2015-11-30 fundamentals/impl.tex
line 398: adds example of spent fuel cask transport optimization

\Cyclus provides a novel representation of entities in the nuclear fuel cycle
that reflects the reality in international nuclear power: facilities implementing individual fuel cycle technologies, institutions managing those facilities, and regions providing geographical and political context for institutions and facilities. While
few simulators have provided any notion of static regional
effects \cite{huff_next_2010,juchau_modeling_2010}, \Cyclus allows for both regions and institutions to be first-class
agents in simulated fuel cycles. The fundamental interactions for each entity are implemented in a corresponding
archetype class in \Cyclus, i.e., the \Class{Region} class, \Class{Institution}
class, and \Class{Facility} class. Archetype developers can then build on the
provided functionality by inheriting from the appropriate class.
\Cyclus implements a \gls{RIF} relationship through a
parent-child hierarchy where
regions are the parents of institutions which are, in turn, the parents of
facilities. In other words, \gls{RIF} hierarchies form a directed acyclic graph (DAG),
with regions as root nodes and facilities as leaf nodes.

@@

Fleet-based, lumped-material models do not distinguish between discrete facility
entities or materials. However, some questions require resolution at the level
of individual facilities and materials.  As a result, many detailed performance
metrics cannot be captured with previously existing fleet-based models. For all
of the reasons that the \gls{ABM} paradigm in \ref{sec:abm} enables novel
simulations, multiple use cases require that these agents, such as the regions,
institutions, and facilities in \Cyclus, must be represented as discrete
objects. For instance, tracking of individual shipments is only viable if materials and
resources are tracked as discrete objects.

>>>>

\Cyclus provides a novel representation of entities in the nuclear fuel cycle
that reflects the reality in international nuclear power: facilities implementing individual fuel cycle technologies, institutions managing those facilities, and regions providing geographical and political context for institutions and facilities. While
few simulators have provided any notion of static regional
effects \cite{huff_next_2010,juchau_modeling_2010}, \Cyclus allows for both regions and institutions to be first-class
agents in simulated fuel cycles. The fundamental interactions for each entity are implemented in a corresponding
archetype class in \Cyclus, i.e., the \Class{Region} class, \Class{Institution}
class, and \Class{Facility} class. Archetype developers can then build on the
provided functionality by inheriting from the appropriate class.
\Cyclus implements a \gls{RIF} relationship through a
parent-child hierarchy where
regions are the parents of institutions which are, in turn, the parents of
facilities. In other words, \gls{RIF} hierarchies form a \gls{DAG},
with regions as root nodes and facilities as leaf nodes.

@@

Fleet-based, lumped-material models do not distinguish between discrete facility
entities or materials. However, some questions require resolution at the level
of individual facilities and materials. As a result, many detailed performance
metrics cannot be captured with previously existing fleet-based models. For 
example, to meaningfully optimize the cost and environmental impact of spent 
nuclear fuel storage, transport, and disposal strategies, discrete casks and 
their varying isotopic compositions must be taken into account.

For all
of the reasons that the \gls{ABM} paradigm in \ref{sec:abm} enables novel
simulations, multiple use cases require that these agents, such as the regions,
institutions, and facilities in \Cyclus, must be represented as discrete
objects. For instance, tracking of individual shipments is only viable if materials and
resources are tracked as discrete objects.
